Group 9 Paper

### 2021-12-16 paper.Rmd
Knitted

@@

```{r SVM_radial}
SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4)

@@

#table(preds,test$HeartDisease)

@@

>>>>

```{r , include=FALSE}

#installation for the reprtree package.
options(repos='http://cran.rstudio.org')
have.packages <- installed.packages()
cran.packages <- c('devtools','plotrix','randomForest','tree')
to.install <- setdiff(cran.packages, have.packages[,1])
if(length(to.install)>0) install.packages(to.install)

library(devtools)
if(!('reprtree' %in% installed.packages())){
  install_github('araastat/reprtree')
}
for(p in c(cran.packages, 'reprtree')) eval(substitute(library(pkg), list(pkg=p)))

@@

```{r SVM_radial}
train <- read.csv("train.csv")
test <- read.csv("test.csv")
train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)
test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)

SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4,type="C")

@@

table(preds,test$HeartDisease)

@@

## References

Banerjee M, Ding Y, Noone AM. Identifying representative trees from ensembles. Stat Med. 2012 Jul 10;31(15):1601-16. doi: 10.1002/sim.4492. Epub 2012 Feb 3. PMID: 22302520.
